Naturalness in U(1) extensions of the MSSM

### 2014-12-03 paper/e6ssm-tuning-paper.tex
Started adding master formula expressions to appendix

\begin{equation}\label{eq:E6masterformula}
\frac{\Delta_p}{2|p|}=\bigg|\tilde{\Delta}_\lambda\frac{\partial\lambda}{\partial p}+\tilde{\Delta}_{A_\lambda}\frac{\partial A_\lambda}{\partial p}+\tilde{\Delta}_{m_{H_d}^2}\frac{\partial m_{H_d}^2}{\partial p}+\tilde{\Delta}_{m_{H_u}^2}\frac{\partial m_{H_u}^2}{\partial p}+\tilde{\Delta}_{m_S^2}\frac{\partial m_S^2}{\partial p}\bigg|.
Explicit expressions for the $\tilde{\Delta}_i$ appearing above are given in Appendix \ref{app:masterformula}. It should be noted that variations in the gauge couplings are neglected in Eq. (\ref{eq:E6masterformula}), so that the formula above is valid at the level of 1-loop RG running and provided that the gauge couplings are excluded from the set $\{p_i\}$. In general, any dimensionless SUSY parameters in $\{p_i\}$ will contribute to the running of the gauge couplings at 2-loops and so terms proportional to $\partial g_i /\partial p$ are also present. For dimensionless $p$, the resulting contributions are $\mathcal{O}(g_1^2p^2)$, $\mathcal{O}(g_1'^2p^2)$, $\mathcal{O}(g_2^2p^2)$ or higher order, and can therefore usually be safely neglected.\\ \\

@@

>>>>

\be
\Delta_p=|C|^{-1}\times \frac{|p|}{M_Z}\bigg|\sum_{q}\tilde{\Delta}_q\frac{\partial q}{\partial p}\bigg|,
\label{eq:E6masterformula}
\ee
where the sum is over all low energy running parameters appearing in the tree level EWSB conditions, i.e. $q\in\{\lambda, A_\lambda, m_{H_d}^2,m_{H_u}^2,m_S^2,g_1,g_2,g_1'\}$. Explicit expressions for the function $C$ and the $\tilde{\Delta}_q$ appearing above are given in Appendix \ref{app:masterformula}. It should be noted that the effects of $U(1)$ mixing are neglected in deriving Eq. (\ref{eq:E6masterformula}).\\ \\

@@

To write down the tree level master formula, it is convenient to define the quantities
\begin{eqnarray}
z_1 &=& \frac{\partial f_2}{\partial s}\frac{\partial f_3}{\partial \tan\beta}-\frac{\partial f_2}{\partial \tan\beta}\frac{\partial f_3}{\partial s}\nonumber\\
z_2 &=& \frac{\partial f_3}{\partial s}\frac{\partial f_1}{\partial \tan\beta}-\frac{\partial f_3}{\partial \tan\beta}\frac{\partial f_1}{\partial s}\nonumber\\
z_3 &=& \frac{\partial f_1}{\partial s}\frac{\partial f_2}{\partial \tan\beta}-\frac{\partial f_1}{\partial \tan\beta}\frac{\partial f_2}{\partial s}\nonumber,
\end{eqnarray}
with $f_1,f_2,f_3$ as given in Eq. (\ref{eq:E6EWSBConditions}). For a running parameter $q$ appearing in the tree level EWSB conditions, the corresponding contribution to the sensitivity coefficient may be written 
\be
\tilde{\Delta}_q=z_1\frac{\partial f_1}{\partial q}+z_2\frac{\partial f_2}{\partial q}+z_3\frac{\partial f_3}{\partial q}.
\label{eq:tuningContribution}
\ee
Similarly, the quantity $C$ appearing in Eq. (\ref{eq:E6masterformula}) is given by
\be
C=\frac{1}{2}\Big ( z_1\frac{\partial f_1}{\partial M_Z}+z_2\frac{\partial f_2}{\partial M_Z}+z_3\frac{\partial f_3}{\partial M_Z}\Big ).
\label{eq:tuningDenominator}
\ee
